\documentclass[titlepage, 12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{comment}
\usepackage{a4wide}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\usepackage{setspace}
\usepackage{epstopdf}

\onehalfspacing

\graphicspath{{./figures/}}

\title{Evolution of sex in Artificial Life using NEAT \\ \large Natural Computing Project Report}
\author{Jules Kruijswijk \\ s4140023 \and Paul Bertens \\ s4512448}
\date{\today}

\begin{document}

\maketitle

\tableofcontents

\newpage

\begin{abstract}
In the vast area of theories on evolution of sex, there are a few interesting theories which touch on the advantages of sexual reproduction over asexual reproduction.
However, it still remains a question why sexual reproduction is as common as it is in the natural world.
Using digital life simulations in Avida, it was found that sexual reproduction is more advantageous in rapid changing environments (a rapid changing environment is an environment where nutrient and poisonous food are swapped, where poison becomes nutrient food and vice versa).
In this report we try to extend this hypothesis to a more ecologically valid situation, but with the same question and hypothesis.
Our research question is if sexual reproduction is more advantageous in a fast changing environment than in a static environment in the used simulation.
An Artificial Life simulation was developed where the agents had neural networks as brains.
The neural networks were evolved using the NeuroEvolution of Augment Topologies (NEAT) algorithm, which evolves the neural networks in their topologies and the assessed weights.
The environment that was created consisted of poisonous and nutrient food, which, as their names suggests, either reduce or increase the energy of an agent.
The experiment consisted of two conditions, one condition where the environment was kept static (thus the food did not swap) and the second condition where the environment was dynamic.
The results showed that the amount of sexual reproduction (measured in average crossover per run, with a total of 30 runs per condition) is significantly more in the dynamic condition than in the static condition ($p = 0.00006335$).
Various ways to investigate the findings and improve the results are highlighted in the discussion section.
\end{abstract}

\input{1-introduction.tex}

\input{2-methods.tex}

\input{3-results.tex}

\input{4-discussion.tex}

\bibliography{bib}
\bibliographystyle{ieeetr}

\end{document}